---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

show_path <- function(path) {
  writeLines(fs::path_rel(path))
}
```

# From MVP to production

If you wanted to build a skyscraper, you'll intuitively know that you can't do
it yourself. You'll need help to know what to do, how to do it, and how long it
will take. Even if you wanted, civil-engineering regulations would stop you. But
software engineering is relatively new, few people intuitively know how complex
it can be, and no regulation would stop you for trying yourself.

The goal of this article is to help a data science team to better understand how
software evolves from a Minimum Viable Product (MVP) to production -- from a
script that "works for me" to an R package that works for anyone anywhere.

> Refactoring is a disciplined technique for restructuring an existing body of code, altering its internal structure without changing its external behavior.

> Its heart is a series of small behavior preserving transformations. Each
transformation (called a "refactoring") does little, but a sequence of these
transformations can produce a significant restructuring. Since each refactoring
is small, it's less likely to go wrong. The system is kept fully working after
each refactoring, reducing the chances that a system can get seriously broken
during the restructuring.

-- https://refactoring.com/

The book [R packages (2e)](https://r-pkgs.org) shows how to refactor R code to
extract the hidden [package within](https://r-pkgs.org/package-within.html) an
analysis script.

Based on that example, this article expands the focus beyond the focal code. It
includes the infrastructure and tests that support the process before, during,
and after refactoring the focal code.

Contents:

1. Reproduce: Making the focal code reproducible from a single executable
script.

2. Snapshot: Capturing key outputs to characterize current behaviour.

3. Refactor: Restructuring the code and testing the external behaviour doesn't
change.

4. Improve: Changing the external behaviour of the code, e.g. to fix bugs.

## 1. Reproduce

_Making the focal code reproducible from a single executable
script_

Ensure the original code is reproducible.

```{r echo=FALSE, results='asis'}
path <- fs::path("~/Downloads", "mvp", "README.md")
show_path(path)
```
```{r results='asis', echo=FALSE}
writeLines(readLines(path))
```

Note the data is inside the project:

  * It might be too large to use version control with Git.
  * It might be private, while everything else might be public.

```{r echo=FALSE, comment=""}
fs::dir_tree("~/Downloads/mvp/")
```

Build infrastructure to support automated workflows (see [R packages
(2e)](https://r-pkgs.org/)), e.g.:

* `usethis::create_package()`
* `devtools::check()` (then address errors, warnings, and notes).
* `usethis::use_directory("inst/extdata")`

Copy the code, excluding data.

* You can now use Git to track code versions, regardless the size of the data.
* You can share public code regardless the privacy of the data.

```{bash echo=FALSE, results='markup', comment=""}
git checkout -q 1-reproduce
Rscript -e 'fs::dir_tree()'
git checkout -q main
```

* HACK: Redirect paths to the data with minimal changes.

```{bash echo=FALSE, results='markup', comment=""}
git show 1-reproduce:inst/extdata/mvp.Rmd | head -24 | tail -10
```

## 2. Snapshot

_Capturing key outputs to characterize current behaviour_

* `usethis::use_test("capture-outputs")`

```{bash echo=FALSE, results='markup', comment=""}
git show 2-snapshot:tests/testthat/test-capture-outputs.R
```

```{bash echo=FALSE, results='markup', comment=""}
git show 2-snapshot:R/utils.R
```

Snapshots

```{bash echo=FALSE, results='markup', comment=""}
git show 2-snapshot:tests/testthat/_snaps/capture-outputs.md
```

New files

```{bash echo=FALSE, results='markup', comment=""}
git checkout -q 2-snapshot
Rscript -e 'fs::dir_tree("tests")'
git checkout -q main
```

WARNING: Don't share snapshots of private data! You may use a dedicated
tests/testthat/private/ directory, add it to .gitignore and test it with
`test_dir(test_path("private"))`.

## 3. Refactor

_Restructuring the code and testing the external behaviour doesn't
change_

inst/extdata/mvp.Rmd

```{bash echo=FALSE, results='markup', comment=""}
git show 3-refactor:inst/extdata/mvp.Rmd | head -28 | tail -14
```

R/

```{bash echo=FALSE, results='markup', comment=""}
git show 3-refactor:R/celsify_temp.R
```

tests/

```{bash echo=FALSE, results='markup', comment=""}
git show 3-refactor:tests/testthat/test-celsify_temp.R | tail -15
```

## 4. Improve

_Changing the external behaviour of the code, e.g. to fix bugs_

* Discuss the current behaviour.
* Fix bugs.
* Remove duplication.
* Implement new behaviour.

```{bash echo=FALSE, results='markup', comment=""}
git show 4-improve:R/celsify_temp.R | tail -11
```

tests/

```{bash echo=FALSE, results='markup', comment=""}
git show 4-improve:tests/testthat/test-celsify_temp.R | tail -4
```

## Enjoy

```{r child="vignettes/articles/cleaning-swimming-data.Rmd"}

```

